Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-07-09 doc/paper.tex
fixed rest of wills comments

Finally, note that the PSD that defines the inner
product \eqref{innerProduct} is simply the time-averaged sensitivity
of a given detector to a specific frequency.  Ignoring non-Gaussian
glitches, any stretch of data should contain a specific noise
realization drawn from a Gaussian colored by the PSD.  Without a
realistic model including the actual instrument sensitivity, non-stationary
 noise, and uncertainty in the PSD we cannot accurately
simulate gravitational-wave data to the point of making precise predictions about
parameter estimation capabilities.  Furthermore, the posterior
distribution from a future detection will be influenced by the
realization of the noise at the time of the detection.  Because of
this, we elect to focus only on the statistical errors due to the
flexibility of the waveforms and the expected sensitivity of the
advanced era detectors and suppress any effects of detector noise by
picking the (most likely) noise realization that has $n(t) \equiv 0$.
Consequently, what we recover with the MCMC could be interpreted as
the posterior distribution function for each source averaged over all
possible (Gaussian) noise realizations, assuming we have the correct
PSD.  \will{This is not true because the map from noise realization to
  posterior is not linear.}

@@

We have performed the current analysis on zero-noise injections for
two reasons.  First, the results of a zero-noise analysis are
identical to those that would be achieved by averaging the results of
multiple identical injections in different Gaussian noise
realizations, as was argued in Section \ref{waveformSection}.
\will{Again, this is not true!}  The second reason is we are not able
to predict the characteristics of realistic (often non-Gaussian)
advanced detector noise.  Attempting to do so would have little chance
of being accurate while requiring a huge computational burden to
combine the results of many MCMC runs in different noise realizations.

In the case of a unique Gaussian realization of the Advanced LIGO
noise curve, each realization causes the maximum likelihood of the
posterior probability distribution to be translated away from the true
value; however, these displacements are drawn from the same probability
distribution we are attempting to sample with the MCMC \citep{Inadequacies}.
 \will{I don't understand
  what ``drawn according to the zero-noise distribution'' means.  I
  don't think this sentence makes sense.} \carl{Changed the sentence, but
   I think you, Tyson, and I will need to chat about this}.  These displacements average to 
   zero over many runs, ensuring that the mean uncertainties should be equal to 
   the uncertainty drawn from the zero-noise runs.  \will{Again, not strictly true.}

>>>>

Finally, note that the PSD that defines the inner
product \eqref{innerProduct} is simply the time-averaged sensitivity
of a given detector to a specific frequency.  Ignoring non-Gaussian
glitches, any stretch of data should contain a specific noise
realization drawn from a Gaussian colored by the PSD.  Without a
realistic model including the actual instrument sensitivity, non-stationary
 noise, and uncertainty in the PSD we cannot accurately
simulate gravitational-wave data to the point of making precise predictions about
parameter estimation capabilities.  Furthermore, the posterior
distribution from a future detection will be influenced by the
realization of the noise at the time of the detection.  Because of
this, we elect to focus only on the statistical errors due to the
flexibility of the waveforms and the expected sensitivity of the
advanced era detectors and suppress any effects of detector noise by
picking $n(t) \equiv 0$.
Consequently, what we recover with the MCMC could be interpreted as
the posterior distribution function for each source averaged over all
possible (Gaussian) noise realizations, assuming we have the correct
PSD and that the signal is sufficiently powerful for the linearized-signal
approximation \citep{Vallisneri} to be valid.

@@

We have performed the current analysis on zero-noise injections for
two reasons.  First, the results of a zero-noise analysis are
similar to those that would be achieved by averaging the results of
multiple identical injections in different Gaussian noise
realizations, as was argued in Section \ref{waveformSection}.  The second reason 
is we are not able
to predict the characteristics of realistic (often non-Gaussian)
advanced detector noise.  Attempting to do so would have little chance
of being accurate while requiring a huge computational burden to
combine the results of many MCMC runs in different noise realizations.

In the case of a unique Gaussian realization of the Advanced LIGO
noise curve, each realization causes the maximum likelihood of the
posterior probability distribution to be translated away from the true
value.  These displacements tend to cancel 
    over many runs, ensuring that the mean uncertainties should be nearly identical to 
   the uncertainty drawn from the zero-noise runs.  Again, this only holds in the case
  where a signal is sufficiently loud that the posterior is linear in the parameters 
  $\thpara$.
